%! Author = mario
%! Date = 25.01.2023

\section{Introduction}\label{sec:introduction}
Machine learning (ML) is a subset of Artificial Intelligence (AI) that focuses on the development of algorithms and statistical
models that allow computers to learn from data and make predictions or judgments without being explicitly programmed.
Reinforcement Learning is a type of Machine Learning that focuses on teaching agents to make decisions in a given environment
by maximizing a reward signal.
It is a method for an agent to learn how to behave in a given situation by executing specific
actions and watching the rewards that the environment provides.\\
ML and RL are widely used in a range of applications, such as robotics, autonomous vehicles, finance, healthcare and games.
This report explores Reinforcement Learning in the latter one, by creating a complex and agility focused labyrinth environment,
that an agent has to successfully solve.
With the help of Unity's ML-Agents~\cite{juliani2020} a model is trained using the standard Reinforcement Learning and Curriculum Learning approach.
The goal of this project was to explore the process of an agent learning a fine motor task.
The following chapter will explain the setup of the board game in real life and as a game in the Unity engine~\cite{Haas2014AHO} to lay the grounds
for the third chapter, where the reinforcement learning aspects of this project are described.
The focus is on the environment and training setup, as well as the reward engineering.
In chapter four the used metrics are discussed and the results presented, in order to give a qualified statement in chapter five
about the performances and show where the process can be improved.